MonteCarlo Simulation's of the Covid-19 Pandemic

### 2022-12-15 paper.rmd

In the study, to fit the data, the authors stated that they used a function of the type of the Gauss error function, that is, the integral of a normal, Gaussian distribution: 
$$a+b*erf(c*x-d)$$

>>>>

In the study, to fit the data, the authors stated that they used a function of the type of the Gauss error function, that is, the integral of a normal, Gaussian distribution:

$$a+b*erf(c*x-d)$$
